% LaTeX resume using res.cls
\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\setlength{\topmargin}{-0.6in}  % Start text higher on the page
\setlength{\textheight}{9.8in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header
\usepackage{fancyhdr}  % use fancyhdr package to get 2-line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\lhead{\hspace*{-\sectionwidth}Stephen Wattam} % force lhead all the way left
\rhead{Page \thepage}  % put page number at right
\cfoot{}  % the footer is empty
\pagestyle{fancy} % set pagestyle for the documenti

\usepackage{tikz}   % Draw the nice footer
\usetikzlibrary{decorations.fractals}
\newcommand{\footersep}{
    \begin{center}
        \begin{tikzpicture}
            \draw [
                gray,
                line width = 0.01mm,
            ](-0.05\linewidth, 0) -- (0, 0);
            \draw [
                gray,
                decoration = Koch curve type 2,
                line width = 0.01mm,
            ] decorate{ decorate{ (0, 0) -- (0.05\linewidth, 0) }};
            \draw [
                gray,
                line width = 0.01mm,
            ](0.05\linewidth, 0) -- (0.1\linewidth, 0);
        \end{tikzpicture}
    \end{center}
}

\begin{document}
\thispagestyle{empty} % this page does not have a header
\name{Stephen Wattam}
\address{\\
\texttt{\ \ \ \ \ <steve@watt.am>}\\
\texttt{http://stephenwattam.com/}}
%     222 South Main Street\\
% North Adams, MA 01247\\
% (413) 555 - 8610}


\begin{resume}
\vspace{0.2in}
\moveleft.5\sectionwidth\centerline{\it Curriculum Vit\ae~---~19-03-2018}

\section{EDUCATION}
\vspace{0.1in}


    Lancaster University, Ph.D,
    \textit{``Technological Advances in Corpus Sampling Methodology''}
    2010--2015

    Lancaster University, MRes,
    Applied Social Statistics,
    \textit{``Folksonomies as Document Summary \mbox{Engines}''}
    2009--2010

    Lancaster University, BSc (Hons),
    Computer Science Innovation,
    \textit{``Adapting Speculative Execution for High-level Distributed Processing''}
    2006--2009



\section{RELEVANT EMPLOYMENT}
\vspace{0.1in}

    {\bf Director},
    WAP Academic Consultancy Limited,
    Oct. 2016--Present\\ 
    Consultancy for NLP as applied to security projects.  Please enquire in person for more details.

    {\bf Lead Scientist},
    Upside Energy Limited,
    Oct. 2016--Present\\
    Design and proof-of-concept of predictive analytics, command \& control systems for distributed energy store.

    {\bf Lecturer},
    Digital Humanities, Centre for Corpus Approaches to Social Science,
    Lancaster University,
    Oct. 2015--Jul. 2016\\
    Publications regarding social science/applied linguistics.

    {\bf Senior Research Associate},
    NLID6 Project, Security Lancaster, School of Computing \& Communications
    Lancaster University,
    Oct. 2015--Feb. 2017\\
    Design and implementation of statistical NLP system for detecting native language influence.

    {\bf Research Associate},
    IAM Development Grant, School of Computing \& Communications
    Lancaster University,
    Apr 2015--Oct. 2015.\\
    Design and implementation of web services API for Wmatrix analysis system.

    {\bf Research Associate},
    SAMUELS project, School of Computing \& Communications
    Lancaster University,
    Oct. 2014--Apr 2015.\\
    Design and implementation of large-scale historical word-sense-disambiguation NLP toolchain.

    {\bf Research Associate},
    Centre for Corpus Approaches to Social Science (CASS),
    Lancaster University,
    Oct. 2014--Apr 2015.\\
    Development of linguistic analysis tools.

    {\bf Senior Research Associate},
    Centre for Corpus Approaches to Social Science (CASS),
    Lancaster University,
    2013--2014.\\
    Design and implementation of `big data' corpus construction \& analysis tools.

    {\bf Research Assistant},
    School of Computing and Communications,
    Lancaster University,
    2013--2014.\\
    Development of NLP toolchain components; crowdsourced data acquisition \& web scraping.

    {\bf Teaching Assistant},
    School of Computing and Communications,
    Lancaster University,
    2009--2017.\\
    Modules: \textsl{Advanced Programming}, \textsl{Fundamentals of Computer Science}, \textsl{Languages \& Compilation}, \textsl{Web Technologies}, \textsl{Operating Systems}, \textsl{Computer Networks}.

    {\bf Freelance Projects}
    \begin{itemize}
        \item Scuttlebutt---Web scraping for linguistic data
        \item Data processing and front-end for the Metaphors in End-of-life Care (MELC) project
        \item Web scraping projects for multiple clients
        \item Porting an NLP toolchain to tag the Hansard corpus
        \item Sylword syllable counting tool
    \end{itemize}

    {\bf Consultant},
    Momote ltd.
    2008 (May--Oct)\\
    Development of web-based vehicle tracking software using Rails \& Prototype.




\section{SKILLS}
\vspace{0.1in}

   {\bf Technical Management (Agile/Academic)}
   \begin{itemize}
        \item Experience in line management of small teams undertaking research/data science workflows
        \item Focus on finding value in interdisciplinary work, comfortable collaborating with and managing those who know more than me
   \end{itemize}

   {\bf Software Development}
        \begin{itemize}
            \item[] Platforms: Linux \& UNIX derivatives, modest server administration experience
            \item[] Languages:
                \begin{itemize}
                    \item Imperative: Python, Ruby, C, ASM (x86, 64--bit)
                    \item Markup: [X]HTML, YAML, XML, \LaTeX
                    \item Other: Bash, R, Brainfuck, Haskell, [Less]CSS, Regexp
                \end{itemize}
            \item[] Tools: Git, SVN, Vim, Selenium
            \item[] Frameworks: Sinatra, JQuery[UI]
        \end{itemize}

  {\bf Pragmatic Problem Solving}
    \begin{itemize}
      \item[] Able to use influences from numerous academic fields and schools-of-thought to find novel solutions to technical problems.
      \end{itemize}

  {\bf Writing}
    \begin{itemize} % Use \item[] to prevent a bullet from appearing
      \item[] Academic papers, technical reports, system documentation.
        Published papers in the field of computational linguistics and cybersecurity.
      \end{itemize}

  {\bf Teaching \& Presenting}
    \begin{itemize}
      \item[] Have delivered numerous conference presentations and lectures in academic and professional settings.
    \end{itemize}

   %{\bf Research and Consulting}
   % \begin{itemize}
   %     \item[] Work on a number of projects as a research assistant, managed small freelance projects.
   % \end{itemize}


\section{PUBLICATIONS}
\vspace{0.1in}


% TODO

% ACL security paper with Martin Bor (via Upside)

% Paper with Yiannis:
% Artificial Intelligence and Machine Learning Approaches to Energy Demand-Side Response: A Systematic Review
% Renewable & Sustainable Energy Reviews

% DERMOT publications with Sheryl?

% Methods paper with Paul Whaley?

% Paper with Mahmoud about crowd sourcing
%\textsl{Using Crowdsourcing to Build Multilingual Semantic Lexicons},


% Sergio's CIRED paper/poster --- https://www.cired-repository.org/handle/20.500.12455/178
Elizondo, S; Wattam, S; Robu, V; Jones, R; Oakes, G:
\textsl{``A Smart Contracting Framework for Aggregators of Demand-Side Response''}
\textit{International Conference on Electricity Distribution (CIRED) 2019}
June 2019


% Scott's SAMUELS paper
S. Piao, F. Dallachy, A. Baron, J. Demmen, S. Wattam, P. Durkin, J. McCracken, P. Rayson and M. Alexander:
\textsl{``A time-sensitive historical thesaurus-based semantic tagger for deep semantic annotation''}
\textit{Computer Speech \& Language 46} (pp.113-135)
November 2017

P. Rayson, J. Mariani, B. Anderson-Cooper, A. Baron, D. Gullick, A. Moore, S. Wattam
\textsl{``Towards Interactive Multidimensional Visualisations for Corpus Linguistics''}
\textit{Journal for Language Technology and Computational Linguistics} (pp.27-49)
May 2017

M. El-Haj, P. Rayson, S. Piao, S. Wattam:
\textsl{Creating and validating multilingual semantic representations for six languages: expert versus non-expert crowds},
Proceedings: \textit{1st Workshop on Sense, Concept and Entity Representations and their Applications: EACL 15} (pp61-71)
April 2017

M. Edwards, S. Wattam, P. Rayson, A. Rashid:
\textsl{``Sampling labelled profile data for identity resolution''}
Proceedings: \textit{IEEE BigData 2016} (pp.540-547)
December 2016

M. Alexander, A. Baron, F. Dallachy, S. Piao, P. Rayson, S. Wattam:
\textsl{``Semantic Tagging and Early Modern Collocates''},
Proceedings: {\it Corpus Linguistics 2015},
Lancaster University
July 2015

P. Rayson, A. Baron, S. Piao, S. Wattam:
\textsl{``Large-scale Time-sensitive Semantic Analysis of Historical Corpora''},
Software demo: {\it International Computer Archive of Modern and Medieval English 36},
Trier,
May 2015

V. Brezina, T. McEnery, S. Wattam:
\textsl{``Collocations in context: A new perspective on collocation networks''},
{\it International Journal of Corpus Linguistics},
July 2015,\\
Proceedings {\it Corpus Linguistics 2015},
Lancaster University, 
July 2015\\
Presented at: {\it Sino-UK Symposium of Corpus Linguistics},
Shanghai Jiao Tong University,
December 2014


J. Alexander, J. Hardy, S. Wattam, :
\textsl{``Characterising the Physicality of Everyday Buttons``},
Proceedings: {\it ACM Interactive Tabletops and Surfaces '14},
Dresden,
September 2014


S. Wattam, P. Rayson \& D. Berridge:
\textsl{``Experiences Parallelising an Existing NLP Pipeline: Tagging Hansard''},
Proceedings: {\it Language Resources and Evaluation '14},
Reykjavik,
May 2014


S. Wattam, P. Rayson \& D. Berridge:
\textsl{``Using Life-Logging to Re-Imagine Representativeness in Corpus Design''},
Proceedings: {\it Corpus Linguistics '13},
Lancaster,
May 2013


S. Wattam, P. Rayson \& D. Berridge:
\textsl{``LWAC: Longitudinal Web as Corpus''},
Proceedings: {\it ACL SIGWAC Web-as-Corpus 8},
Lancaster,
May 2013


S. Wattam, P. Rayson \& D. Berridge:
\textsl{``Document Attrition in Web Corpora: an Exploration''},
Proceedings: {\it Language Resources and Evaluation '12},
Istanbul,
May 2012


S. Wattam, P. Rayson \& D. Berridge:
\textsl{``Folksonomies as Document Summary Engines''},
Proceedings: {\it Corpus Linguistics '11},
Birmingham,
July 2011



% \section{TEACHING}
%
% S. Wattam, A. Moore, P. Rayson:
% \textbf{Web Scraping},
% UCREL Summer School lectures and practicals.
%
% S. Wattam & J.Vidler:
% \textbf{Automata in the Real World},
% \texttt{stephenwattam.com/teaching/maize/}\\
% Maze solving using state machines: tools and practical tasks.
% 
% S. Wattam, C. Ellis \& contributors:
% \textbf{Maize},
% \texttt{stephenwattam.com/projects/Maize}\\
% Maze generation and algorithmics: tool and lectures.
%
% S. Wattam \& R. Larson:
% \textbf{Server Compromise Case Study},
% Guest lecture analysing an SSH break-in, including hands-on use of tools.
%



\footersep

\end{resume}
\end{document}
